Future challenges for Research Software Engineering

### 2025-04-07 future_challenges_for_RSEng.tex
use semantic line breaks, no content change
avoid potential line break before citation

RSEs are publicly funded.
Like data collected by scientists should adhere to the FAIR principles \cite{FAIR}, research software developed by RSEs
should adhere to the FAIR4RS principles \cite{FAIR4RS}.

>>>>

RSEs are publicly funded.
Similarly to how data collected by scientists should adhere to the FAIR principles \cite{FAIR}, research software developed by RSEs should adhere to the FAIR4RS principles~\cite{FAIR4RS}.
